%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Avinash Roy} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:8800932794}{+91 8800932794}
    $|$
    \faAt \hspace{.5pt} \href{mailto:avin.roy001@gmail.com}{avin.roy001@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/avinash-roy-73aa597b/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/avinroy001}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://www.crio.do/learn/portfolio/avin-roy001/?edit=true}{Portfolio}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://maps.app.goo.gl/aqxroPZMkGD1uSbz8}{Patna, India}
\end{center}
%----------- EDUCATION -----------
\section {Summary}
Versatile and motivated Computer Science Engineer with a solid foundation earned through a Bachelor's degree in 2013. My journey has been unconventional, marked by different ventures. Now equipped with a diverse skill set and a rich portfolio of projects, I am eager to transition into the dynamic landscape of the software industry.
\vspace{-10pt}
%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{OS:}{ MacOS, Basics of Linux Commands} \\ \vspace{3pt}
        
        \textbf{Languages:}{ JavaScript, HTML, CSS, ES6} \\ \vspace{3pt}
        
        \textbf{Technologies/Framework:}{ REST API, Node.js, React.js, Bootstrap, MaterialUI, DOM Manipulation, JSON} \\ \vspace{3pt}
        
        \textbf{Tools:}{ Git, Render, Netlify, Figma, Vercel, Thunder client} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd
    \vspace{-15pt}
%----------- EXPERIENCE -----------

\section{EXPERIENCE }
  \resumeSubHeadingListStart
  \resumeSubheading{CRIO.DO}{May 2023 -- Present}
  {Fellowship in software Development}{}
  % \vspace{-20pt}
  \resumeItemListStart 
  \resumeItem{Developed and implemented full stack web applications as part of the crio.do curriculum.}
  \resumeItem{Gained hands-on experience with technologies such as HTML, CSS, JavaScript, Node.js, Express, MongoDB, etc.}
  \resumeItem{Collaborated with a team of developers to work on real-world projects, simulating industry scenarios.}
  \resumeItem{Applied best practices in software development, including version control (Git) methodologies.}
  \resumeItem{Participated in code reviews and provided constructive feedback to peers.}
  \resumeItemListEnd
  \resumeSubHeadingListEnd
  \vspace{-15pt}
  
%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{QTify} $|$ \emph{\href{https://l-square-q-tify-ashy.vercel.app/}{\color{blue}GitHub}}}{Jan 2024}
          \resumeItemListStart
            \resumeItem{Conducted a thorough analysis of the provided Figma design, successfully identifying and documenting required front-end components.}
            \resumeItem{Created modular UI components including Cards, Carousels, and Buttons optimizing for reusability across various sections of the application.}
            \resumeItem{Implemented an intuitive genre-based song filtering system using a tab component by modifying the one provided by MaterialUI, allowing users to browse songs by their preferred genre effortlessly.}
            \resumeItem{Utilized REST APIs to fetch data served by the backend server}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{QKart Frontend} $|$ \emph{\href{https://qkart-frontend-eight-fawn.vercel.app/}{\color{blue}GitHub}}}{Dec 2023}
          \resumeItemListStart
            \resumeItem{Implemented the core logic for authentication, shopping cart and checkout.}
            \resumeItem{Improved UI by adding responsive design elements for uniform experience across different devices.}
            \resumeItem{Utilized REST APIs to dynamically load and render data served by the backend server.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{XBoard} $|$ \emph{\href{https://avinroy001-xboard.netlify.app/}{\color{blue}GitHub}}}{Oct 2023}
          \resumeItemListStart
            \resumeItem{Built XBoard using HTML, CSS, Bootstrap and JavaScript from scratch.}
            \resumeItem{Used Accordions and Image Carousel to improve UI.}
            \resumeItem{Fetched news content from flipboard's RSS feed using REST API.}
          \resumeItemListEnd

          \resumeProjectHeading
        {\textbf{QTripDynamic} $|$ \emph{\href{https://avin-001qtripdynamic.netlify.app/}{\color{blue}GitHub}}}{Sep 2023}
          \resumeItemListStart
            \resumeItem{Created web pages using HTML and CSS and made them dynamic using JavaScript.}
            \resumeItem{Improved UX with multi-select filters, image carousels.}
            \resumeItem{Utilised localStorage to persist user preferences at client-side.}
          \resumeItemListEnd

          \resumeProjectHeading
        {\textbf{QTripStatic} $|$ \emph{\href{https://avinroy001-qtrip.netlify.app/}{\color{blue}GitHub}}}{Aug 2023}
          \resumeItemListStart
            \resumeItem{Created 3 different web pages from Wireframe layout using HTML and CSS.}
            \resumeItem{Utilized Bootstrap extensively for responsive design.}
            \resumeItem{Deployed the website to Netlify/Vercel.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd

%----------- EDUCATION -----------

\section {EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dr. B.C Roy Engineering Engineering College}{Durgapur, West Bengal}
      {Bachelor of Engineering in Computer Science }{Aug. 2009 -- July. 2013}
      	\resumeItemListStart
    	\resumeItem {\textbf{DGPA}: 6.83}
        \\ {(Degree Grade Point Average)}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}